---
title: "Mcap_parents Data Wrangle"
author: "Shayle Matsuda"
date: "1/17/2022"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Script analyzing ITS2 for Mcap parents in Kaneohe Bay
Data processed in Symportal

```{r}
#library
library(janitor)
library(phyloseq)  # source('http://bioconductor.org/biocLite.R'); biocLite('phyloseq')
library(zoo)
library(stringr)
library(vegan)
library(multcompView)
library("ggpubr")
library(readxl)
library("writexl")
library(tidyverse)
```

# Relative Abundance 
Read in coral ITS2 profiles: "coral"
```{r}  
#add metadata to symportal submission data
Symp_sub<-readxl::read_xlsx("data/ITS2_Mcap_Ford_Feb2023.xlsx", skip = 1)
Metadata<-read.csv("data/Mcap_parents_metadata.csv") #121C is 1212C
Metadata<-rename(Metadata, sample_name=Sample.ID) #rename UNIQUEID column to sample_name
Symp_sub_Meta<-left_join(Symp_sub, Metadata, by="sample_name") # merge
#save in correct format:
write_xlsx(Symp_sub_Meta,"ITS2_Mcap_Ford2022b.xlsx")

sam0 <- readxl::read_xlsx("ITS2_Mcap_Ford2022b.xlsx") #Symportal metadata combined from above
sam1 <- as.matrix(sam0[, -1])
rownames(sam1) <- sam0$sample_name
sam <- sample_data(data.frame(sam1))

tax0 <- read_tsv(
  file  = "data/its2_type_profiles/190_20220112_03_DBV_20220114T140414.profiles.relative.abund_and_meta.txt",
  n_max = 6) %>%
  dplyr::select(-2) %>% 
  gather(UID, value, -1) %>% 
  spread(1, value) %>%
  clean_names()

tax1 <- as.matrix(tax0[, -1], dimnames = list(tax0$uid, colnames(tax0[-1])))
rownames(tax1) <- tax0$uid
tax <- tax_table(tax1)

otu0 <- read_tsv(
  file  = "data/its2_type_profiles/190_20220112_03_DBV_20220114T140414.profiles.relative.abund_and_meta.txt") %>% 
  rename(sample_name = 2) %>%  # this used to be X2 for some reason now it's just 2
  select(-1) %>%
  slice(7:n()) %>%
  mutate_at(2:ncol(.), as.numeric)
otu1 <- as.matrix(otu0[, -1])
rownames(otu1) <- otu0$sample_name
otu <- otu_table(otu1, taxa_are_rows = FALSE)

coral <- phyloseq(otu, tax, sam)
```
Read in coral post-QC sequence variants: "coralDIV"
```{r}  
sam0 <- read_xlsx("ITS2_Mcap_Ford2022b.xlsx")
rownames(sam0) <- sam0$sample_name
sam <- sample_data(data.frame(sam0))

taxnames <- read_tsv(
  file  = "data/post_med_seqs/190_20220112_03_DBV_20220114T140414.seqs.relative.abund_only.txt",
  n_max = 0) %>%
  select(-1) %>%
  names(.)
tax0 <- data_frame(
  DIV = taxnames,
  clade = str_extract(DIV, "[A-Z]")
)
tax1 <- as.matrix(tax0)
rownames(tax1) <- tax0$DIV
tax <- tax_table(tax1)

otu0 <- read_tsv(
  file  = "data/post_med_seqs/190_20220112_03_DBV_20220114T140414.seqs.relative.abund_only.txt") %>%
  select(-1, )
otu1 <- as.matrix(otu0[, -1])####### you changed this not sure what select(3:33) was about
rownames(otu1) <- sam0$sample_name
otu <- otu_table(otu1, taxa_are_rows = FALSE)
coralDIV <- phyloseq(otu, tax, sam)
```

#Quality Check - remove low samples
```{r}
coral2 <- coral %>% 
  subset_samples(!is.na(host_species))
coralDIV2 <- coralDIV %>% 
  subset_samples(!is.na(host_species))

# Transform to relative abundance after raw reads checks
#coral2 <- transform_sample_counts(coral2, function(x) 100 * x/sum(x))
#coralDIV2 <- transform_sample_counts(coralDIV2, function(x) 100 * x/sum(x))


```

Data wrangle: remove samples with under 1500 
```{r} 
LowSamps<-readxl::read_xlsx("data/post_med_seqs/190_20220112_03_DBV_20220114T140414.seqs.absolute.meta_only.xlsx")
LowSamps$post_taxa_id_absolute_symbiodiniaceae_seqs_log<-log10(LowSamps$post_taxa_id_absolute_symbiodiniaceae_seqs)
hist(LowSamps$post_taxa_id_absolute_symbiodiniaceae_seqs_log, breaks=30)
```
Look at the low samples: no patterns
```{r} 
sample_names(coralDIV2) #print sample names
#look at NTCs
#Negative Controls
  NTCtest <- subset_samples(coralDIV2, sample_name =="PCR-Neg1"| sample_name =="PCR-Neg2") #subset multiple samples
   NTCtest.prune <- prune_taxa(taxa_sums(NTCtest) >0, NTCtest)
     plot_bar(NTCtest.prune,fill = "DIV")+
      geom_bar(aes(color=DIV, fill=DIV), stat="identity", position="stack")
     
#Samples under 1500 hits removed
LOWtest <- subset_samples(coralDIV2, 
                            sample_name =="10A"| 
                            sample_name =="1255A"|
                            sample_name =="1263A"|
                            sample_name =="1263B"|
                            sample_name =="141B"|
                            sample_name =="146C"|
                            sample_name =="160C"|
                            sample_name =="353C"|
                            sample_name =="386C"|
                            sample_name =="620C"|
                            sample_name =="684C"|
                            sample_name =="70B"|
                            sample_name =="745C")
                             #subset multiple samples

   LOWtest.prune <- prune_taxa(taxa_sums(LOWtest) >0, LOWtest) # prune all 0s
     
   plot_bar(LOWtest,fill = "DIV")+                     # plot DIVS
    geom_bar(aes(color=DIV, fill=DIV), stat="identity", position="stack")
     
   plot_bar(LOWtest,fill = "clade")+                     # plot Clades
      geom_bar(aes(color=clade, fill=clade), stat="identity", position="stack")
```
 
Remove low samples from the datasets (samples with less than 1500)
```{r} 
#DIVs 
to_remove <- c("PCR-Pos1", "PCR-Pos2", "PCR-Neg1", "PCR_Neg2","353C","684C", "386C","10A","146C","1263B","620C","745C","70B","1255A","146B","1263A","160C") #make list of samples to remove with less than 1299 seqs
# "1261C","485B","315A","333C" add backin if less than 1500
#"151C","497C","141C","576B","620A","70A","141B","83B" add back in if 2k cutoff

coralDIV2.prune <- prune_samples(!(sample_names(coralDIV2) %in% to_remove), coralDIV2) #remove
#sample_names(coralDIV2.prune) # check to see they are removed

#Pros
coral2.prune <- prune_samples(!(sample_names(coral2) %in% to_remove), coral2) #remove
#sample_names(coral2.prune) # check to see they are removed

```

Save as RData
```{r} 
save(coral, coralDIV, file = "data/coral_phyloseq.RData")
```
